Model Search in Relational Domains

### 2016-10-20 experiments.tex
description of result

We verified a total of 66 benchmarks in ANSI-C, which are derived from 
(a) bit-vector regression category in SV-COMP'16, (c) bit-precise and 
cycle accurate software models of hardware circuits automatically 
generated using v2c~\cite{mtk2016}, (c) controller code generated 
from Simulink (d) several hand-crafted benchmarks for equivalence 
checking and bounded loop analysis.  All bounded loops are completely 
unrolled before analysis.  We compare our tool with a state-of-the-art 
SAT-based bounded model checker CBMC~\cite{cbmc} and a commercial 
static analysis tool, Astr{\'e}e.  CBMC uses MiniSAT solver in the backend.  
Astr{\'e}e was configured with default set of domains which includes 
interval, bit-field, congruence, trace partitioning and relational 
domains (octagons, polyhedra, zones, equalities, filter).

\Omit {
To enable precise analysis using Astr{\'e}e, all our benchmarks are 
manually instrumented with partition directives which provides external 
hint to the tool to guide the trace partitioning heuristics.  Usually, 
such high-precision is not needed for static analysis, since it makes 
the analysis very expensive.  Without trace partitioning, the 
analysis using Astr{\'e}e shows high degree of imprecision. 
}
\paragraph {\textbf{Precision and Efficiency of Analysis}}
Figure~\ref{fig:results} presents a comparison of the analysis 
using CBMC and ACDCL.  The cumulative statistics corresponding to 
each phase of the algorithm for all 66 benchmarks is presented in 
Table~\ref{result}.  Experimental result shows a reduction of at least 
two orders of magnitude in the number of decisions, propagations and conflicts 
compared to analyis using CBMC.    
%
\begin{table}
\begin{center}
{
\begin{tabular}{l|l|l|l|l|l}
\hline
Solver & Decisions & propagations & conflict & conflict literals & restarts \\ \hline
SAT & 27917 & 304031 & 3949 & 33646 & 64 \\ \hline
ACDCL (Product Domain) & 161 & 3130 & 10 & 5 & 0 \\ \hline  
\end{tabular}
}
\end{center}
\caption{Solver statistics}
\label{result}
\end{table}
%
Out of 66 benchmarks, CBMC with MiniSAT backend could only prove 16 benchmarks 
without any restarts.  The solver is restarted in 50 cases to avoid spending 
too much time in branches that does not easily lead to a satisfying assignment or 
stronger clause learning.  In contrast, the analysis using ACDCL solved all
66 benchmarks without any restarts.  This is attributed to intelligent decision 
heuristics which exploits the high-level structure of the program combined 
with stronger deductions and clause learning mechanism aided by the richer 
abstract domains.  On the other hand, Ast{\'e}e is often faster than ACDCL, 
but the analysis using Astr{\'e}e shows high degree of imprecision.  
Astr{\'e}e reported 15 false alarms out of 41 safe benchmarks.

>>>>

We verified a total of 66 benchmarks in ANSI-C, which are derived from 
(a) bit-vector regression category in SV-COMP'16, (c) bit-precise and 
cycle accurate software models of hardware circuits automatically 
generated using v2c~\cite{mtk2016}, (c) controller code generated 
from Simulink (d) several hand-crafted benchmarks for equivalence 
checking and bounded loop analysis.  All bounded loops are completely 
unrolled before analysis.  We compare our tool with a state-of-the-art 
SAT-based bounded model checker CBMC~\cite{cbmc} and a commercial 
static analysis tool, Astr{\'e}e.  CBMC uses MiniSAT solver in the backend.  
Astr{\'e}e was configured with range of abstract domains which includes 
interval, bit-field, congruence, trace partitioning and relational 
domains (octagons, polyhedra, zones, equalities, filter).  Whereas, 
ACDCL was instantiated with a product domain of booleans and template 
polyhedra.   
%
\Omit {
To enable precise analysis using Astr{\'e}e, all our benchmarks are 
manually instrumented with partition directives which provides external 
hint to the tool to guide the trace partitioning heuristics.  Usually, 
such high-precision is not needed for static analysis, since it makes 
the analysis very expensive.  Without trace partitioning, the 
analysis using Astr{\'e}e shows high degree of imprecision. 
}
\paragraph {\textbf{Precision and Efficiency of Analysis}}
Figure~\ref{fig:results} presents a comparison of the analysis 
using CBMC and ACDCL.  Figure~\ref{fig:results}(a) clearly shows that 
the SAT solver made significantly more decisions compared to ACDCL 
for all the benchmarks.  Whereas, the extreme right points below the 
diagonal in Figure~\ref{fig:results}(b) shows the propagations in SAT solver  
is maximum for the benchmarks that exhibit relational behavior.  The 
cumulative statistics corresponding to each phase of the algorithm 
for all 66 benchmarks is presented in Table~\ref{result}.  
Experimental result shows a reduction of at least two orders of 
magnitude in the number of decisions, propagations and conflicts 
compared to analyis using CBMC.    
%
\begin{table}
\begin{center}
{
\begin{tabular}{l|l|l|l|l|l}
\hline
Solver & Decisions & propagations & conflict & conflict literals & restarts \\ \hline
SAT & 27917 & 304031 & 3949 & 33646 & 64 \\ \hline
ACDCL (Product Domain) & 161 & 3130 & 10 & 5 & 0 \\ \hline  
\end{tabular}
}
\end{center}
\caption{Solver statistics}
\label{result}
\end{table}
%
Out of 66 benchmarks, CBMC with MiniSAT backend could only prove 16 benchmarks 
without any restarts.  The solver is restarted in 50 cases to avoid spending 
too much time in branches that does not easily lead to a satisfying assignment or 
stronger clause learning.  In contrast, the analysis using ACDCL solved all
66 benchmarks without any restarts.  This is attributed to intelligent decision 
heuristics which exploits the high-level structure of the program combined 
with stronger deductions and clause learning mechanism aided by the richer 
abstract domains.  On the other hand, Ast{\'e}e is often faster than ACDCL, 
but the analysis using Astr{\'e}e shows high degree of imprecision.  
Astr{\'e}e reported 15 false alarms out of 41 safe benchmarks.
